\documentclass{res}

\usepackage[T1]{fontenc}
\usepackage{textcomp,multicol}
\usepackage[hidelinks]{hyperref}
\usepackage[bottom=1em,top=3em,left=3em,right=5.5em]{geometry}

\begin{document}
\name{\hspace{-2.5em}Sean DuBois}
\address{\href{maihto:sean@siobud.com}{\hspace{-1em}sean@sioBuD.com} \\ \href{http://github.com/sean-der}{\hspace{-1em}GitHub.com/Sean-Der}}

\begin{resume}
\vspace{1em}

\section{\centerline{EXPERIENCE}}

\href{https://apple.com/}{{\it Apple}} - Technology company that specializes in electronics, software, and online services.  \hfill {\bf 2020 - *\space \space \space}
\begin{itemize}  \itemsep -2pt
    \item Built FaceTime links, service that allows users to join FaceTime from a web browser
    \item Designed and implemented media Quality of Service subsystems
\end{itemize}

\href{https://amazon.com/}{{\it Amazon}} - American electronic commerce and cloud computing company \hfill {\bf 2018 - 2020\space \space \space}
\begin{itemize}  \itemsep -2pt
    \item Designed and implemented Pure C WebRTC implementation for embedded devices
    \item Worked on Chromium on Android/Linux/Windows, the foundation for Amazon Silk
    \item Added support for Mediatek WebRTC H264 encoding on Android
\end{itemize}

\href{https://infiniscene.com/}{{\it Infiniscene}} - broadcast studio built on the web \hfill {\bf 2016 - 2018}
\begin{itemize}  \itemsep -2pt
    \item Wrote cloud compositing engine, ingestion of many sources and output to many destinations
    \item Created ingestion engine, handles multiple popular transports RTP/UDT/SRT/RTMP
    \item Deep WebRTC usage, worked with ICE/DTLS/Custom signaling in GStreamer
    \item Created H264 analyzer to educate users, parsing byte-stream to warn about unsupported features
    \item Updated developer tooling, moved developers over to shared Docker workflow
\end{itemize}

\href{https://www.etsy.com/}{{\it Etsy}} - e-commerce website focused on handmade {\bf \hfill 2014 - 2016}
\begin{itemize}  \itemsep -2pt
    \item Improved \href{https://github.com/elasticsearch/kibana}{{\it Kibana}}, adding aggregations and features for internal use
    \item Worked on internal IRC client that aimed to humanize users, adding proprietary extensions
    \item Upgraded Etsy to PHP 7, which involved porting multiple language extensions written in C
\end{itemize}

\href{http://www.onshored.com}{{\it onShore Development}} - Creator of Webcheckout, an scheduling and asset management application {\bf \hfill 2013 - 2014 }
\begin{itemize}  \itemsep -2pt
    \item Converted Web App to be API driven, using Common Lisp and PostgreSQL on the backend
    \item Ported frontend to Angular/Bootstrap, replacing projects in Dojo and jQuery
\end{itemize}

\href{http://www.saicorporate.com}{{\it System Associates}} - Developer of full stack software and hardware for major hotels {\bf \hfill 2011 - 2016 }
\begin{itemize}  \itemsep -2pt
    \item Used Asterisk with custom Dialplan and Applications written in C to create a hosted PBX
    \item Created a deployment system using git so updates and new installs can be done seamlessly
    \item Developed a web interface to manage PBX
\end{itemize}

\section{\centerline{PROJECTS}}
\vspace{1em}
\href{https://github.com/pion/webrtc}{{\bf Pion WebRTC}} - \it{Pure Golang implementation of WebRTC.} \\
\textup{Creator, Implemented SRTP, SCTP, STUN and ICE. No 3rd party library usage.}\\
\\
\href{https://webrtcforthecurious.com}{{\bf WebRTC for the Curious}} - \it{A book on how WebRTC really works.} \\
\textup{Author, learn about the protocols of WebRTC. A book that goes beyond the APIs.}\\
\\
\href{https://github.com/awslabs/amazon-kinesis-video-streams-webrtc-sdk-c}{{\bf amazon-kinesis-video-streams-webrtc-sdk-c}} - \it{Embedded WebRTC Implementation} \\
\textup{Designed and worked with team of 5 to implement. Used in IoT/Robotics.}\\
\\
\href{https://gstreamer.freedesktop.org}{{\bf GStreamer}} - \it{Free pipeline-based multimedia framework.} \\
\textup{Added \href{https://github.com/GStreamer/gst-plugins-bad/commits/master/ext/aom}{{\bf AV1}} support. Fixed bugs, added flvmux feature}\\
\\
\href{https://php.net}{{\bf PHP}} - \it{Scripting language especially suited to web development.} \\
\textup{Added \href{https://wiki.php.net/rfc/class_const_visibility}{{\bf class constant visibility}} to the language. Ported msgpack, oauth, yaml and others to PHP 7}\\
\\
\href{https://janus.conf.meetecho.com}{{\bf Janus}} - \it{WebRTC gateway, mostly used for relaying RTP} \\
\textup{Added ECDSA Cert generation, fixed bugs, small streaming features}\\
\\
\href{https://www.chromium.org/}{{\bf Chromium}} - \it{open-source Web browser project started by Google} \\
\textup{Added support for Mediatek WebRTC H264 encoding on Android}\\
\\
\href{https://github.com/Sean-Der/fail2web}{{\bf fail2web}} - \it{fail2ban GUI, written with Go and AngularJS.} \\
\textup{Creator, contributed to \href{https://github.com/fail2ban/fail2ban}{{\bf fail2ban}} and \href{https://github.com/kisielk/og-rek}{{\bf ogorek}}}\\

\end{resume}
\end{document}
